Computational musicology, ????, Profit

### 2016-08-14 paper.tex
Add keywords.
Fix title case in heading.
Balance the columns of the final page.
Add country to affiliation.
Add category.

\usepackage{amsmath}
\usepackage{hyperref}

@@

\authorinfo{Chris Ford}
           {ThoughtWorks}
           {christophertford@gmail.com}

@@

%\category{CR-number}{subcategory}{third-level}

%\keywords
%keyword1, keyword2

@@

\section{Analysis by compression}

@@

\acks

>>>>

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{balance}

@@

\authorinfo{Chris Ford}
           {ThoughtWorks UK}
           {christophertford@gmail.com}

@@

\category{J.5}{Arts and Humanities}{Arts, fine and performing}

\keywords
computational musicology, musicology, complexity theory, kolmogorov complexity, literature, algorave

@@

\section{Analysis by Compression}

@@

\balance
\acks
